\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}

### 2023-03-29 paper/main_preprint.tex
Reorganize papers

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{gfx}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

\author{Alec Hoyland, Nelson V. Barnett, Benjamin W. Roop, Danae Alexandrou, Myah Caplan, Jacob Mills, Benjamin Parrell, Divya A. Chari, and Adam C. Lammert\textsuperscript{\textdagger{}}%
\thanks{This work was supported in part by the University of Massachusetts
Center for Clinical and Translation Science.}%
\thanks{A. Hoyland is with the Department of Biomedical Engineering (BME)
at Worcester Polytechnic Institute (WPI), Worcester, MA and with Clarifai, Inc., Wilmington, DE.
N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
B.W. Roop is formerly of the Neuroscience Program at WPI, now with  MIT Lincoln Laboratory, Lexington, MA.
D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, Chicago, IL.
B. Parrell is with the Department of Communication Sciences and Disorders and the Waisman Center at University of Wisconsin, Madison, WI. D.A. Chari is with the
University of Massachusetts Chan Medical School, Worcester, MA
and the Massachusetts Eye and Ear Infirmary,
Boston, MA.
The authors declare no competing interests.}%
\thanks{\textsuperscript{\textdagger{}} Corresponding Author}}%

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
% TC:ignore
\begin{abstract}
  \textit{Goal:} This study validates a reverse correlation method for characterizing the sounds experienced by tinnitus patients with potential for characterizing a wider range of sounds than currently possible.
  \textit{Methods:} Ten normal-hearing subjects assessed the subjective similarity of random auditory stimuli and target tinnitus-like sounds (“buzzing” and “roaring”).
  Reconstructions of the targets were obtained by regressing subject responses on the stimuli, and were compared for accuracy to the frequency spectra of the targets using Pearson's $r$.
  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing ($M=0.53$, $SD=0.27$): $t(9)=5.766$, $p<0.001$; roaring ($M=0.57$, $SD=0.30$): $t(9)=5.76$, $p<0.001$.
  \textit{Conclusion:} Reverse correlation can accurately reconstruct non-tonal tinnitus-like sounds in normal-hearing subjects,
  indicating its potential for characterizing the sounds experienced by patients with non-tonal tinnitus.
% The purpose of this document is to illustrate how one should prepare manuscripts for submission to the IEEE Open Journal of Engineering in Medicine and Biology (OJEMB). Please notice that this is the template for TECHNOLOGY LETTERS. These are short manuscripts with primary focus on the development of new devices, methods, and technologies. The material must be organized in a main manuscript body and a section entitled Supplementary Materials. The main manuscript body should be limited to 1,000 words and the material should be organized in the following sections (in the order shown here): Introduction, Materials and Methods, Results, Discussion, Conclusions. Authors can include in the main manuscript body up to 3 display items (i.e. figures and tables). In addition, the main manuscript body should include an abstract and up to 20 references. The references are not considered in the 1,000-word count. The abstract should be organized in subsections as shown here (i.e., Goal, Methods, Results, Conclusions). An impact statement should be included. The impact statement should be a short paragraph of no more than 30 words. Additional material should be included in the Supplementary Materials section of the manuscript. The Supplementary Materials section should either be organized in sections as per the main manuscript body (using up to 4,000 words) or it should be used to provide readers with a set of up to 10 additional display items (i.e. figures and tables). \textit{Methods}: Use this document as a template if you are using Latex. Otherwise, use this document as an instruction set. \textit{Results}: Paper titles should be written in uppercase and lowercase letters as shown above. Do not cite references in the abstract. Do not delete the blank line immediately above the abstract; it sets the footnote at the bottom of this column. The abstract should not exceed 150 words. \textit{Conclusions}: Preparing carefully your manuscript will lead to enhanced readability.
\end{abstract}

@@

%TC:ignore
\begin{minipage}[t]{0.9\columnwidth}
  \textbf{\textit{Impact Statement}\textemdash{}Characterization of tinnitus can inform tinnitus treatment by allowing for individualized sound therapies, leading to better outcomes for patients suffering from the cognitive and psychological effects of tinnitus.}\\
\\
\end{minipage}
%TC:endignore

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound
in the absence of any corresponding external stimulus\textemdash{}affects up to 50 million people in the U.S. \cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
a third of whom experience functional cognitive impairment and substantial reduction in quality of life
\cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like external sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or in the context of Cognitive Behavioral Therapy \cite{tunkelClinicalPracticeGuideline2014}.
Critically, sound therapy is shown to improve with knowledge of the patient's internal tinnitus experience \cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020}.
However, existing strategies for characterizing tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients who experience sounds resembling pure tones (\eg ringing).
This group may represent only between 20-50\% of all tinnitus patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017}, with others experiencing non-tonal (\eg buzzing, roaring) tinnitus sounds.
There is a pressing need for more robust tinnitus characterization methods \cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.

% INTRO PARAGRAPH 2/3
Tinnitus sounds are presumed to be both complex and heterogeneous
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020,meikleTinnitusArchiveArchive2004},
although little has been firmly established about the specific characteristics.
Therefore, we base our approach on \textit{reverse correlation} (RC),
an established behavioral method
\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
for probing internal representations of visual and auditory percepts that is unconstrained by prior knowledge about the percepts themselves.
RC asks subjects to render subjective judgments (\eg “does this sound like your tinnitus?”)
over random stimuli, 
from which unbiased estimates of the percepts can be produced.
RC is closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
which has also inspired ``white-noise'' approaches to system characterization in physiology
\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering more broadly
\cite{ljungMeasureLackFit1978}.

% INTRO PARAGRAPH 3/3
Here, we validate RC as a method for characterizing all component
frequencies of non-tonal tinnitus sounds
by estimating the full psychoacoustic tinnitus spectrum (PTS).
To that end, we asked normal-hearing participants to complete an augmented RC experiment, comparing random stimuli to a target tinnitus-like sound.
Target sounds were subsequently used as the basis for validating the quality of the estimated PTS.
Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC. 
This discovery may open the door to developing a clinical assay for characterizing the full range of sounds experienced by tinnitus patients.

@@

Software code used for the experiments and analysis was written in MATLAB and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-reconstruction/}.

\subsection{Stimuli}

Stimuli were composed of $b=8$ Mel-spaced frequency bins,
which divide the frequency spectrum between $[100,~13,000]$
Hz into continuous segments of equal amplitude (\ie ``rectangular'' bins).
Reconstruction detail increases with $b$, but $b=8$ bins provides a good approximation to the chosen target sounds (see Fig. \ref{fig:spectra}).

For each stimulus, $[2,7]$ bins were randomly ``filled'' with power $0$ dB. ``Unfilled'' bins were assigned a power of $-100$ dB. 
Assigning random phase, the inverse Fourier transform of the spectrum yields a $500$-ms stimulus waveform.

\subsection{Target Sounds}

Two tinnitus-like target sounds (``buzzing'' and ``roaring'') from online examples maintained by the American Tinnitus Association
\cite{MeasuringTinnitusAmerican2022} were downloaded and truncated to $500$-ms in duration. These sounds were selected for the complexity and complementary nature of their frequency spectra.

\subsection{Experiment}

Trials followed an $A-X$ paradigm (Fig. \ref{fig:experimentdiagram}), where $n=10$ subjects with self-reported normal hearing listened to the same target sound ($A$) followed by a random stimulus ($X$) for each trial.
The task is designed to mimic the process by which a tinnitus patient might compare a random stimulus to their own tinnitus percept.

Subjects were told that some stimuli had the target sound embedded in them, and were instructed to respond ``yes'' to any such stimuli, and ``no'' otherwise.
Subjects performed trials in blocks of $100$, with breaks between blocks.
Subjects completed two ($2$) blocks of trials per given target, $A$.
The $400$ total trials took subjects 10-20 minutes to complete.

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{experiment_overview.pdf}
  \caption{Diagram of the experimental protocol.
  Subjects listen to a series of random stimuli,
  each preceded by a target sound.
  Subjects compare the stimulus to the target, and respond either ``yes'' or ``no''
  depending on their perceived similarity.
  The recorded stimulus-response pairs are used to form an estimate of the target.}
  \label{fig:experimentdiagram}
\end{figure}

\subsection{Reconstruction}

@@

where $x \in \mathbb{R}^\mathrm{b}$ represents the subject's internal representation of interest (\eg their tinnitus percept).
This model can be inverted, yielding the following formula:

@@

This formula is a restricted form of the Normal equation, under
the assumption that the stimulus dimensions are uncorrelated \cite{gosselinSuperstitiousPerceptionsReveal2003}.
Intuitively, $\hat{x}$ is the sum of all stimuli eliciting a ``yes'' response, after subtracting all stimuli eliciting a ``no.''

\subsection{Validation}

The $A-X$ paradigm allows for direct validation of the reconstructions $\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ against their corresponding target sounds.
To that end, we represent the power spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same $b=8$ frequency bins used in stimulus generation.
The power in each bin is set as the mean power level of frequencies within that bin.
Pearson's $r$ between $s_{buzzing}$ and $s_{roaring}$ and their corresponding reconstructions ($\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$) represents reconstruction accuracy.
One-sample t-tests were performed on the mean Fisher-transformed $r$ values across subjects to assess significant differences from zero.

\subsection{Synthetic and Random Subjects}

To establish bounds on human performance,
additional experiments were run \textit{in-silico} with two simulated subjects that
represent participants who always give either \textit{ideal} or \textit{random} responses.
Each experiment ran for $n=200$ trials and was repeated $1000$ times.

@@

% NB NOTE: What is s??
for $i \in 1, ..., n$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
$\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
The ideal subject represents one who has precise knowledge of every stimulus and where the reconstruction algorithm mirrors \ref{eq:linreg}.

@@

where $X \in [0, 1]$ is a uniform random variable.

\section{Results}

Figure \ref{fig:reconstructions} shows the distribution of Pearson's $r$ (\ie reconstruction accuracy) from human, ideal, and random subject responses in the buzzing and roaring experimental conditions.
Accuracies from human responses were generally higher than those from random subject responses,
with some accuracies approaching those from ideal subject responses.
Mean accuracy from the random subject responses was $0$ in all conditions,
while mean accuracy from human responses was significantly different from $0$ in all conditions: buzzing: $t(9) = 5.766$, $p < 0.001$; roaring: $t(9) = 5.76$, $p < 0.001$; combined: $t(19) = 7.542$, $p < 0.001$.
The buzzing results vary more than the roaring results. The buzzing ground truth spectrum contains significant high-frequency content,
suggesting that the task may be more difficult for subjects with minor high-frequency hearing loss.
Figure \ref{fig:spectra} plots example reconstructions from human responses with the best reconstruction accuracies overlaid on the target sound spectra,
showing that those reconstructions capture many of the salient features of the target.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{reconstruction_violin_1.eps}
    \caption{Reconstruction accuracy for human subjects is significantly above baseline,
    but is not optimal. Reconstruction accuracies of random, human, and ideal subjects
    are shown as violin plots with box plots overlaid.
    The median is a white dot, the ordinate of the blue points are the Pearson's $r$ values.}
    \label{fig:reconstructions}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{reconstruction_spectra.eps}
    \caption{Reconstructions of the PTS capture many salient features of tinnitus spectra.
    On each set of axes, the black trace indicates the target,
    while colored traces plot exemplar reconstructions from human subjects' data.
    In the top row, the target and reconstructions are shown as
    standardized power levels within each frequency bin.
    In the bottom row, those standardized power levels are mapped from the $8$-dimensional bin domain
    to a $11025$-dimensional frequency domain.
    The unbinned power spectral density of the targets is also shown in gray.}
    \label{fig:spectra}
\end{figure}

\section{Conclusion}

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{gfx_preprint}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% \author{Alec Hoyland, %,~\IEEEmembership{Fellow, IEEE,}
%         Samantha Peznola, and Adam C. Lammert% <-this % stops a space
% \thanks{Paper submitted on DATE.
% 	This work was supported in part by the University of Massachusetts
% 	Center for Clinical and Translational Science Pilot Project Program 2022,
% 	grant number GRANT_NUMBER.
% 	Alec Hoyland is a graduate student in the Department of Biomedical Engineering
% 	at Worcester Polytechnic Institute (WPI), Worcester, MA, USA;
% 	Samantha Peznola is a Research Assistant at WPI;
% 	and Dr. Adam C. Lammert is Assistant Professor of Biomedical Engineering at WPI.
% }}
% \author{Alec Hoyland, Nelson Barnett, Benjamin W. Roop, and Adam C. Lammert\textsuperscript{\textdagger{}}%
\author{Alec Hoyland, Nelson V. Barnett, Benjamin W. Roop, Danae Alexandrou, Myah Caplan, Jacob Mills, Benjamin Parrell, Divya A. Chari, and Adam C. Lammert\textsuperscript{\textdagger{}}%
\thanks{This work was supported in part by the University of Massachusetts
Center for Clinical and Translation Science.}%
\thanks{A. Hoyland is with the Department of Biomedical Engineering (BME)
at Worcester Polytechnic Institute (WPI), Worcester, MA and with Clarifai, Inc., Wilmington, DE.
N.V. Barnett, M. Caplan, J. Mills and A.C. Lammert are also with BME at WPI.
B.W. Roop is formerly of the Neuroscience Program at WPI, now with  MIT Lincoln Laboratory, Lexington, MA.
D. Alexandrou is with the Stritch School of Medicine at Loyola University Chicago, IL.
B. Parrell is with the Department of Communication Sciences and Disorders and the Waisman Center at University of Wisconsin, Madison, WI. D.A. Chari is with the
University of Massachusetts Chan Medical School, Worcester, MA
and the Massachusetts Eye and Ear Infirmary,
Boston, MA.
The authors declare no competing interests.}%
\thanks{\textsuperscript{\textdagger{}} Corresponding Author}}%
% NB NOTE: This is mentioned at the top of Materials and Methods. Should be just one or the other. 
% I like the footnote better, but the footnote could be moved to MM section. 
% \thanks{Code is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-project/}.
% Data are available upon request.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  \textit{Goal:} This study validates a method for characterizing the sounds experienced by tinnitus patients with potential for characterizing a wider range of sounds than currently possible.
  The approach is based on reverse correlation, an established behavioral method widely used in psychophysics for unconstrained characterization of internal perceptual representations.
  \textit{Methods:} Ten normal-hearing subjects participated in a reverse correlation experiment, where they assessed the subjective similarity of random auditory stimuli and target tinnitus-like sounds (“buzzing” and “roaring”).
  Reconstructions of the targets were obtained by regressing subject responses on the stimuli, and were compared for accuracy to the frequency spectra of the targets using Pearson's $r$.
  \textit{Results:} Reconstruction accuracy was significantly higher than chance across subjects: buzzing: $0.52 \pm 0.27$ (mean $\pm$ s.d.), $t(9) = 5.766$, $p < 0.001$;
  roaring: $0.62 \pm 0.23$, $t(9) = 5.76$, $p < 0.001$;
  combined: $0.57 \pm 0.25$, $t(19) = 7.542$, $p < 0.001$.
  \textit{Conclusion:} Reverse correlation can accurately reconstruct non-tonal tinnitus-like sounds in normal-hearing subjects,
  indicating its potential for characterizing the sounds experienced by patients with non-tonal tinnitus.
% The purpose of this document is to illustrate how one should prepare manuscripts for submission to the IEEE Open Journal of Engineering in Medicine and Biology (OJEMB). Please notice that this is the template for TECHNOLOGY LETTERS. These are short manuscripts with primary focus on the development of new devices, methods, and technologies. The material must be organized in a main manuscript body and a section entitled Supplementary Materials. The main manuscript body should be limited to 1,000 words and the material should be organized in the following sections (in the order shown here): Introduction, Materials and Methods, Results, Discussion, Conclusions. Authors can include in the main manuscript body up to 3 display items (i.e. figures and tables). In addition, the main manuscript body should include an abstract and up to 20 references. The references are not considered in the 1,000-word count. The abstract should be organized in subsections as shown here (i.e., Goal, Methods, Results, Conclusions). An impact statement should be included. The impact statement should be a short paragraph of no more than 30 words. Additional material should be included in the Supplementary Materials section of the manuscript. The Supplementary Materials section should either be organized in sections as per the main manuscript body (using up to 4,000 words) or it should be used to provide readers with a set of up to 10 additional display items (i.e. figures and tables). \textit{Methods}: Use this document as a template if you are using Latex. Otherwise, use this document as an instruction set. \textit{Results}: Paper titles should be written in uppercase and lowercase letters as shown above. Do not cite references in the abstract. Do not delete the blank line immediately above the abstract; it sets the footnote at the bottom of this column. The abstract should not exceed 150 words. \textit{Conclusions}: Preparing carefully your manuscript will lead to enhanced readability.
\end{abstract}

@@

\begin{minipage}[t]{0.9\columnwidth}
  \textbf{\textit{Impact Statement}\textemdash{}Characterization of tinnitus can inform tinnitus treatment by allowing for individualized sound therapies, leading to better outcomes for patients suffering from the cognitive and psychological effects of tinnitus.}\\
\\
\end{minipage}

\section{Introduction}
% INTRO PARAGRAPH 1/3
\IEEEPARstart{T}{INNITUS}\textemdash{}the perception of sound (\eg ringing, buzzing)
in the absence of any corresponding external stimulus\textemdash{}affects over 25 million people in the U.S., with some estimates ranging up to 50 million \cite{bhattPrevalenceSeverityExposures2016,nationalinstituteondeafnessandothercommunicationdisordersQuickStatisticsHearing},
a third of whom experience functional cognitive impairment and substantial reduction in quality of life
\cite{ahmedImpactTinnitusPerception2017,nondahlImpactTinnitusQuality2007,tegg-quinnImpactTinnitusCognition2016}.
Primary treatment options for tinnitus are currently limited by a lack of methods for accurately characterizing the full breadth of internal sounds experienced by patients.
Clinical guidelines for tinnitus management frequently involve targeted exposure to tinnitus-like external sounds, either as a form of habituation therapy (termed \textit{sound therapy}), or in the context of Cognitive Behavioral Therapy, where patients are encouraged to perceive their tinnitus as a neutral stimulus \cite{tunkelClinicalPracticeGuideline2014}.
Critically, treatment outcomes have been repeatedly shown to improve when the external sounds used in sound therapy are closely informed by the internal tinnitus experience of the patient
\cite{davisNeuromonicsTinnitusTreatment2007,landgrebeMethodologicalAspectsClinical2012,nickelOutcomeResearchMusic2005,okamotoListeningTailormadeNotched2010,schaetteAcousticStimulationTreatments2010,steinInhibitioninducedPlasticityTinnitus2015,tassCounteractingTinnitusAcoustic2012,wangStateArtSound2020,neffComparingThreeEstablished2019,schoisswohlAmplitudeModulatedNoise2019}.
However, existing strategies for characterizing the tinnitus sounds, such as Pitch Matching (PM) methods, are best suited for patients with tonal tinnitus, who experience sounds resembling pure tones (\eg ringing).
% However, existing methods for characterizing the tinnitus sounds\textemdash{}Pitch Matching (PM) methods\textemdash{}are best suited for patients with tonal tinnitus, who experience sounds resembling pure tones (\eg ringing).
This group may represent between 50-80\% of all tinnitus patients \cite{turnerjrAuditoryDysfunctionTinnitus1990,henryAuditoryTestResult2009,ukaegbeTinnitusItsEffect2017,vajsakovicPrinciplesMethodsPsychoacoustic2021}, with the other 20-50\% experiencing nontonal (\eg buzzing, roaring) tinnitus sounds.
There is a pressing need for characterization methods targeting tinnitus patients who are not served by current procedures
\cite{henryTinnitusEpidemiologicPerspective2020,henryMeasurementTinnitus2016,norenaPsychoacousticCharacterizationTinnitus2002,robertsResidualInhibitionFunctions2006}.

% INTRO PARAGRAPH 2/3
Tinnitus sounds are presumed to be both complex and heterogeneous
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryTinnitusEpidemiologicPerspective2020,meikleTinnitusArchiveArchive2004},
although little has been firmly established about the specific characteristics.
Therefore, we base our approach on the demonstrated capabilities of \textit{reverse correlation} (RC),
an established behavioral method
\cite{ahumadaStimulusFeaturesSignal1971,gosselinSuperstitiousPerceptionsReveal2003,brimijoinInternalRepresentationVowel2013}
for probing internal representations of visual and auditory percepts that is unconstrained by prior knowledge about the percepts themselves.
RC asks subjects to render subjective judgments (\eg “does this sound like your tinnitus?”)
over random stimuli that have no direct relation to the percepts of interest,
from which correspondingly unbiased estimates of those objects can be produced.
RC is closely related to Wiener theory \cite{wienerNonlinearProblemsRandom1966},
which has also inspired so-called white-noise approaches to system characterization in physiology
\cite{ringachReverseCorrelationNeurophysiology2004,marmarelisWhiteNoiseMethodSystem1978} and engineering more broadly
\cite{ljungSystemIdentificationTheory1998}.

% INTRO PARAGRAPH 3/3
Here, we validate RC as a method for characterizing all component
frequencies of non-tonal tinnitus sounds
by estimating the full psychoacoustic tinnitus spectrum (PTS).
To that end, we asked normal-hearing participants to complete an augmented RC experiment where they had to compare random stimuli to a target tinnitus-like sound.
Target sounds were subsequently used as the basis for validating the quality of the estimated PTS.
Our results demonstrate, for the first time, that tinnitus-like sounds with complex spectra can be accurately estimated using RC. 
This discovery may open the door to developing a clinical assay based on RC for characterizing the full range of sounds experienced by tinnitus patients.

@@

Software code used for the experiments and analysis was written in MATLAB (Mathworks, Inc., Natick, Massachusetts)
and is freely available at \protect\url{https://github.com/alec-hoyland/tinnitus-project/}.
% The code depends on \cite{bechtoldViolinPlotsMatlab2022,kochYaml2022,gorur-shandilyaSrinivasGsMtools2022}.

% ACL, DONE
\subsection{Stimuli}

Stimuli were composed of $b=8$ Mel-spaced frequency bins,
which divide the frequency spectrum between $[100,~13,000]$
Hz into continuous segments of equal amplitude (\ie ``rectangular'' bins).
While $b=8$ bins were found to provide a good approximation to the target sounds used here (see Fig. \ref{fig:spectra}),
more bins results in finer spectral details in the reconstruction as well as increased computational complexity.

To generate a stimulus, we randomly select $[2,7]$ bins with uniform probability to be ``filled'' with power $0$ dB,
while ``unfilled'' bins were assigned a power of $-100$ dB. 
Assigning random phase, we then take the inverse Fourier transform of the spectrum to yield a $500$-ms stimulus waveform.

% ACL, DONE
\subsection{Target Sounds}

Tinnitus-like target sounds were drawn from online examples maintained by the American Tinnitus Association
\cite{MeasuringTinnitusAmerican2022}.
The two examples selected for this study corresponded to those described as ``buzzing'' and ``roaring.''
These sounds were selected for the complexity and complementary nature of their frequency spectra.
These examples were downloaded and truncated to $500$-ms in duration.

% ACL, DONE
\subsection{Experiment}

We recruited $n=10$ subjects with self-reported normal hearing to participate in the experiment.
All procedures were approved by the UMass IRB.
Subjects listened over earphones, and manually adjusted the loudness of presented sounds to a self-determined comfortable level.
Presentation level was not recorded.
Trials followed an $A-X$ presentation paradigm (Fig. \ref{fig:experimentdiagram}),
where subjects listened to a target sound ($A$) followed by a stimulus ($X$).
$A$ remained the same for every trial within a given experimental condition,
while $X$ was randomly generated for each trial.
The task is designed to mimic the process by which a tinnitus patient might compare a random stimulus to their own tinnitus percept in the context of a RC experiment.

Subjects were told that some stimuli had the target sound embedded in them, and were instructed to respond ``yes'' to any such stimuli, and to respond ``no'' otherwise.
Subjects performed trials in blocks of $100$, with breaks between blocks.
% NB QUESTION: Is the (2) necessary? If they don't require it, I'd remove it. 
Subjects completed two ($2$) blocks of trials per experimental condition (\ie for a given target, $A$).
The $400$ total trials took subjects about 10-20 minutes to complete.

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{experiment_overview.pdf}
  \caption{Diagram of the experimental protocol.
  Subjects listen to a series of random stimuli,
  each preceded by a target sound.
  Subjects compare the stimulus to the target, and respond either ``yes'' or ``no''
  depending on their perceived similarity.
  The recorded stimulus-response pairs are used to form an estimate of the target
  using a restricted regression procedure.}
  \label{fig:experimentdiagram}
\end{figure}

% ACL, DONE
\subsection{Reconstruction}

@@

where $x \in \mathbb{R}^\mathrm{b}$ represents the subject's internal representation of interest (\eg their tinnitus percept).
This model can be inverted, yielding the following commonly-used formula for reconstructing internal representations in RC experiments:

@@

This formula is a restricted form of the Normal equation\textemdash{}the least-squares solution to a linear regression problem\textemdash{}under
the assumption that the stimulus dimensions are uncorrelated \cite{gosselinSuperstitiousPerceptionsReveal2003}.
Intuitively, this implies that the reconstruction, $\hat{x}$, is the sum of all stimuli eliciting a ``yes'' response, after subtracting the sum of all stimuli eliciting a ``no.''

% ACL, DONE
\subsection{Validation}

By adopting the $A-X$ paradigm for the present experiments,
we have the opportunity to directly validate the reconstructions
$\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ against their corresponding target sounds.
To that end, we represent the power spectra of the target sounds as vectors $s_{buzzing} \in \mathbb{R}^\mathrm{b}$ and $s_{roaring} \in \mathbb{R}^\mathrm{b}$ using the same $b=8$ frequency bins used in stimulus generation.
The power in each bin is taken to be the mean power level for frequencies contained within that bin.
The vectors $s_{buzzing}$ and $s_{roaring}$ can then be directly compared to their corresponding reconstructions
$\hat{x}_{buzzing}$ and $\hat{x}_{roaring}$ using Pearson's $r$, representing a measure of reconstruction accuracy.
One-sample t-tests were performed on the mean Fisher-transformed $r$ values across subjects to assess significant differences from zero.

% ACL, DONE
\subsection{Synthetic and Random Subjects}

For the purposes of establishing upper and lower bounds on human performance in this experiment,
additional experiments were run \textit{in-silico} with two simulated subjects,
representing a participant who always gives \textit{ideal} responses and one who always gives \textit{random} responses.
Each experiment ran for $n=200$ trials and was repeated $1000$ times.

@@

for $i \in 1, ..., n$, where $Q(x, y)$ is the quantile function for $x \in [0, 1]$ of the similarity calculation $\Psi s$, and
$\Psi_i$ is the $i^\mathrm{th}$ column of $\Psi$.
The ideal subject represents an \textit{upper bound} on task performance,
where the subject has precise knowledge of every stimulus and where the reconstruction algorithm mirrors the subject response model assumed by RC.

@@

where $X \in [0, 1]$ is a uniform random variable.
The random subject represents a \textit{lower bound} on task performance,
where the subject ignores any knowledge of the stimulus, or indeed their own internal representation.

% ACL, DONE
\section{Results}

Figure \ref{fig:reconstructions} shows the distribution of Pearson's $r$ (\ie reconstruction accuracy) from human, ideal, and random subject responses in the buzzing and roaring experimental conditions.
Accuracies from human responses were generally higher than those from random subject responses,
with some accuracies approaching those from ideal subject responses.
Accuracy from the random subject was $0.00 \pm 0.44$ (mean $\pm$ st.dev.) for buzzing and $0.00 \pm 0.39$ for roaring,
while mean accuracy from human responses was significantly different from $0$ in all conditions:
buzzing: $0.52 \pm 0.27$, $t(9) = 5.766$, $p < 0.001$;
roaring: $0.62 \pm 0.23$, $t(9) = 5.76$, $p < 0.001$;
combined: $0.57 \pm 0.25$, $t(19) = 7.542$, $p < 0.001$.
From Figure \ref{fig:reconstructions},
it appears that the distribution of buzzing results differs from that of the roaring results,
however the difference between buzzing and roaring is not statistically significant
(two-way ANOVA across subjects ($F(13) = 2.94$, $p > 0.05$) and target signals ($F(1) = 2.44$, $p > 0.05$)).
The buzzing ground truth spectrum contains significant high-frequency content,
suggesting that the task may vary in difficulty for subjects with different audiograms (\ie for subjects with minor high-frequency hearing loss).
Figure \ref{fig:spectra} shows example reconstructions from the best human responses (as quantified by reconstruction accuracy) overlaid on the target sound spectra,
showing that those reconstructions capture many of the salient features of the target.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{reconstruction_violin_1.eps}
    \caption{Reconstruction accuracy for human subjects is significantly above baseline,
    but is not optimal. Reconstruction accuracies of random, human, and ideal subjects
    are shown as violin plots with box plots overlaid.
    The median is a white dot, the ordinate of the blue points are the Pearson's $r$ values.
    The top row shows accuracies for the buzzing target, the middle row shows accuracies
    for the roaring target signal, and the bottom row shows results for both buzzing and roaring combined.}
    \label{fig:reconstructions}
\end{figure}
